### 2023-09-15 paper/sec-results.tex
update chi2 numbers

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|c|c|c}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & \multirow{2}{*}{Baseline}
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  &  &  2.256  &  2.242   & 2.215   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & & 2.360    &   2.332  & 2.311  \\
  $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$
  & &   1.194   &    1.187    & 1.169  \\
  \midrule
  \multirow{8}{*}{$\chi^2/n_{\rm dat}$}
  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
  & FPF (total)                 &  1.301 / 0.923 &   1.192    &   0.888   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to the variants including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2/n_{\rm dat}$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2/n_{\rm dat}$ over replicas $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$,
  $\chi^2/n_{\rm dat}$ for datasets grouped by process.
  %
  The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset.
  For the baseline fit we present both the value computed with only statistical error
  and also adding the systematics so that it can be compared with both fits. 
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------

The statistical estimators for the NNPDF4.0 NNLO
baseline fit, compared to the variants including
the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
and~\ref{fig:NNPDF40_lowQ_abs}, are reported in Table~\ref{tab:chi2_nnpdf40_baseline}.
%
The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset,
for which one finds $\chi^2/n_{\rm dat} \sim 1$ up to fluctuations, consistent
with the fact that the FPF pseudo-data
is produced by construction to be compatible with the NNPDF4.0 baseline.
%
For the same reason, the description of the other experiments entering
the NNPDF4.0 global fit is not distorted by the inclusion of the FPF data.
%
In particular, the $\chi^2/n_{\rm dat}$ of the available (non-FPF) DIS neutral-current and charged-current
datasets changes from 1.220 and 0.904 in NNPDF4.0 to 1.220 and 0.913 in the fit
with FPF pseudo-data.
%
A moderate increase is found to the $\chi^2/n_{\rm dat}$ of Drell-Yan processes, from 1.76 to 1.83, possibly
because of the enhanced weight that DIS data carries in this fit variant.

>>>>

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|c|c|c}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & \multirow{2}{*}{Baseline}
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2/n_{\rm dat}$ &  \multirow{4}{*}{Global}  & 1.17  &  1.16   & 1.15   \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  &  &  2.26  &  2.24   & 2.21   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & & 2.36    &   2.33  & 2.30  \\
  $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$
  & &   1.19   &    1.19    & 1.16  \\
  \midrule
  \multirow{8}{*}{$\chi^2/n_{\rm dat}$}
  & DIS neutral-current                     &  1.22    &  1.23    &   1.22   \\
  & DIS charged-current                     &   0.90  &   0.94    &  0.90    \\
  & Drell--Yan (inclusive and one-jet)      &  1.76   &   1.83    &   1.83   \\
  & Top-quark pair production               &  1.23   &   1.22    &  1.25     \\
  & Single-top production                   &  0.36    &   0.36   &   0.37    \\
  & Inclusive jet production                &  0.96    &  0.96      &   0.94    \\
  & Dijet production                        &  2.03     &    2.01    &   2.00    \\
  & Direct photon production                 &  0.74   &   0.73     &    0.73   \\
  & FPF (total)                 &  1.30  / 0.92  &   1.19     &   0.89    \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to the variants including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2/n_{\rm dat}$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2/n_{\rm dat}$ over replicas $\la \chi^2/n_{\rm dat}\ra_{\rm rep}$,
  $\chi^2/n_{\rm dat}$ for datasets grouped by process.
  %
  The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset.
  For the baseline fit we present both the value computed with only statistical error
  and also adding the systematics so that it can be compared with both fits. 
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------

The statistical estimators for the NNPDF4.0 NNLO
baseline fit, compared to the variants including
the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
and~\ref{fig:NNPDF40_lowQ_abs}, are reported in Table~\ref{tab:chi2_nnpdf40_baseline}.
%
The last row displays the $\chi^2/n_{\rm dat}$ obtained for the combined FPF dataset,
for which one finds $\chi^2/n_{\rm dat} \sim 1$ up to fluctuations, consistent
with the fact that the FPF pseudo-data
is produced by construction to be compatible with the NNPDF4.0 baseline.
%
For the same reason, the description of the other experiments entering
the NNPDF4.0 global fit is not distorted by the inclusion of the FPF data.
%
In particular, the $\chi^2/n_{\rm dat}$ of the available (non-FPF) DIS neutral-current and charged-current
datasets is unchanged (1.22 and 0.90, respectively) from the baseline to the fit with FPF pseudo-data.
%
A moderate increase is found to the $\chi^2/n_{\rm dat}$ of Drell-Yan processes, from 1.76 to 1.83, possibly
because of the enhanced weight that DIS data carries in this fit variant.
